%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {MSc, Artificial Intelligence} % Degree
    {\newline The University of Stirling} % Institution
    {Scotland} % Location
    {2020-2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Designing, training and tuning state of the art deep learning and vision transformer models for computer vision.}
        \item{Adaptation of new and emerging models and code developed by the current state of the art research.}
        \item{Mathematical skills in probability theory, matrix algebra and stochastic modelling and optimization.}
        \item{An applied understanding of signal processing, unstructured data.}
        \item{Representing and manipulating data using Python (CSV, XML and JSON formats), as well as leveraging RESTful APIs and web-crawling.}
        \item{Data science project design and implementation using predictive, inferential and exploratory statistics.}
        \item{Writing object-oriented software to parallelize and automate data processing and train models.}
      \end{cvitems}
    }
\cventry
    {BA(Hons.), Fine Art Photography (1st Class) } % Degree
    {\newline The Glasgow School of Art } % Institution
    {Scotland} % Location
    {2007-2011} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Understanding of camera and sensor mechanics on digital images.}
        \item{Effective creative ability to think laterally and think creatively.}
        \item{Skilled in Adobe Cloud, Photoshop and InDesign for image manipulation.}
        \item{Advanced understanding of image compression and digital file formats.}
        \item{Visual communication and critical understanding of visual culture.}
        \item{Ability to communicate effectively on the creative continent and concepts. }
      \end{cvitems}
    }
\cventry
    {Art Psychotherapy, Introduction} % Degree
    {\newline The University of Glasgow} % Institution
    {Scotland} % Location
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Working with groups in a therapeutic setting.}
        \item{Understanding the  importance of images in enabling communication.}
        \item{Ability to understand and apply psychological concepts within a group setting.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
