%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://www.stir.ac.uk}{<stir.ac.uk>}\vspace{-5pt} \newline Computer Vision Researcher} % Job title
    {The University of Stirling\vspace{-9pt}} % Organization
    {Stirling, Scotland} % Location
    {2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designing and Adapting state of the art models including vision transformers.}
        \item {Collaborative working to tight deadlines alongside ability to work independently.}
        \item {Extensive knowledge of computer vision libraries such as OpenCV, Kearas, TesorFlow and PyTorch.}
        \item {Contribution to knowledge in the field of computer vision image analysis and digital image processing.}
        \item {Ability to conduct independent research, think algorithmic and apply original thought to challenging complex problems.}
      \end{cvitems}
    }

  \cventry
    {\href{https://www.scottishrefugeecouncil.org.uk/}{<scottishrefugeecouncil.org.uk>}\vspace{-5pt} \newline Refugee Integration Services Manager } % Job title
    {The Scottish Refugee Council\vspace{-9pt}} % Organization
    {Glasgow, Scotland} % Location
    {Apr. 2019 - Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Data analytics and generating business intelligence to support organisation strategic decision making.}
        \item {Developing Sales-force recording systems and managing implementation of object-oriented databases for storing using highly confidential personal data.}
        \item {Managing change and developing front-line refugee integration services in Scotland. }
        \item {Organisational lead on Scottish government strategy and evidence groups. }
        \item {Project management, oversight and accountability for project outputs within multi-agency partnerships. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://www.redcross.org.uk/}{<redcross.org.uk>}\vspace{-5pt} \newline Refugee and Family Integration Manager } % Job title
    {The British Red Cross\vspace{-9pt}} % Organization
    {Glasgow, Scotland} % Location
    {Dec. 2016 - Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Data analytics for service modelling and development. }
        \item {Report writing and editorial oversight of research projects.}
        \item {Managing qualitative research into refugee families’ experiences of integration.}
        \item {CRM database development as part of generating credible data for research, reporting and influencing objectives. }
        \item{Organisational representative on the Scottish government’s New Scots evidence group. }
      \end{cvitems}
    }

%---------------------------------------------------------
%---------------------------------------------------------
  \cventry
    {\href{https://www.redcross.org.uk/}{<redcross.org.uk>}\vspace{-5pt} \newline Refugee Support Casework Coordinator} % Job title
    {The British Red Cross\vspace{-9pt}} % Organization
    {Glasgow, Scotland} % Location
    {Dec. 2012 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Training and managing volunteers in data entry and case-note recording.}
        \item {Developing a new service for refugee families arriving in the UK. }
        \item {Partnership working to develop effective workflows and referral mechanisms. }
        \item{In-depth understanding of public policy across domains of health, immigration law, education, housing, and welfare benefits.}
        \item{Understanding of challenges, security concerns and need for confidentiality and discretion when  working toward objectives to support individuals with complex needs.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
